An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-01 notes/jessie-russian-lemma.tex

>>>>

\section{The story of Lemma 2: a subset of saga.}

\jessie{This isn't quite typechecking for me, with the function $P$.  In their paper, $P$ should be a function of a subset of $\Y$, but for monotonicity, we want it to be the CDF?}

If we want to show $A := \{\E_p V \mid V(y) \in \partial L(u,y) \, p-a.s.\}$ is closed, and do this by showing $A = cl(A)$.  Thankfully, $A \subseteq cl(A)$ follows trivially, so it is left to show $A \supseteq cl(A)$.

Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.

Now define functions $P_m : \Y \to \reals^d$ so that $P_m(y) = \int_E V_m(y') dpy'$, where $E =\{y' \in \Y \mid y' \leq y\}$ and $P_m(y)$ is the CDF of $V_m$.  We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.
We have uniform boundedness from their first past of the result, and monotonicity from each $P_m$ being a CDF

\begin{theorem}[Helly's Theorem]\label{thm:helly}
	A uniformly bounded sequence of monotone real functions admits a (pointwise) convergent subsequence
\end{theorem}

Therefore, for any $z \in \reals^d$, by the Dominated Convergence Theorem \jessie{or Helly-Bray \url{https://en.wikipedia.org/wiki/Helly\%E2\%80\%93Bray_theorem}}, we have 
\begin{align*}
\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy
\end{align*}

In particular, we can now take the selection $V(y) = P(y)$ as the density of $P$.
Define $P_c$ as the singular part of $P$; that is, the region where $P$ is not defined, concentrated on a set of measure zero.

If $P_c$ is empty (i.e., $P$ is defined for all $y \in \Y$)\jessie{I think this is what we need to claim for an everywhere selection}, then for any $z \in \reals^d$, we have
\begin{align*}
\int \inprod{z}{P(y)} dy &= \lim_{m \to \infty} \int \inprod{z}{P_m(y)} dy \leq \int L'(u,y;z) dy
\end{align*}

From this, it follows that $\inprod{z}{V(y)} \leq L'(u,y;z)$ for all $y \in \Y$, and therefore $V(y) \in \partial L(u,y)$ for all $y \in \Y$.

This yields $P(\sup_{y' \in \Y} y) = \int V(y) dy \in \int \partial L(u,y) dpy$.

Therefore, we have 
\begin{align*}
\lim_{m\to \infty} V_m &= V \\
\implies \lim_{m \to \infty} \E_p V_m &= \E_p V \in A\\
\lim_{m \to \infty} v_m &= v \in A
\end{align*}

### 2021-04-01 poly-embed-journal/poly-embed-journal.tex

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks)
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}

>>>>

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}
